---
title: "Resubmit_Analysis"
output: pdf_document

---

```{r include=F}
# will need the private_metadata from the authors
library(plyr)
library(here)
library(tidyverse)
library(ggplot2)
library(readxl)
library(pander)
library(mice)
library(mitml)
library(lme4)

# read in the private metat data
d<-read.csv(here::here("private_metadata.csv"))

### same code as in pre-experiment to make unique IDs ###
# remove the - sign. It causes problems later
d$corpus<-revalue(d$corpus, c("Casillas-Yeli"="CasillasYeli"))
#add a column called with a unique id (the original child id pasted together with the corpus)
d <- d %>% mutate(unique_id = paste0(child_ID, corpus))
#get rid of data from the warlaumont corpus
d <- d %>% filter(corpus != c("Warlaumont"))
#make a new column with the language
d <- d %>% mutate(language = ifelse(corpus == "Seedlings",
                                    "English",
                                    "Non-English"))
#make a categorical age variable based on 07, 8-18, and 19-36 groupings
d <- d %>% mutate(age_groups = ifelse(age_mo_round <= 7,
                                      "0-7",
                                      ifelse(age_mo_round <= 18,
                                             "8-18",
                                             "19-36")))
#make grouping variable for age-language question
d <- d %>% mutate(age_language = paste0(age_groups, language))
#keep only canonical and non-canonical
d <- d %>% filter(Answer %in% c("Canonical", "Non-canonical"))
#### end copy of pre-experiment code #####

metadata<-d

##### TRIAL DATA #####
# get data before exclusions
library(here)
d <- read.csv(here::here("data","trial_data.csv"))
library(ggplot2)

# refactor the group so the order is correct in the graphs
d$stim_ageGroup<-factor(d$stim_ageGroup,levels = c("0-7","8-18","19-36"))

# attatch baby data to trial data
d$stim_age<-rep(0,nrow(d))
for(i in 1:nrow(d)){
  baby_data<-subset(metadata,metadata$clip_ID==d$clipID[i])
  d$stim_age[i]<-baby_data$age_mo_round # age in months
  d$age_error[i]<-min(c(abs(d$stim_age[i]-7.5),abs(d$stim_age[i]-18.5))) #absolute difference between age and closest cut off
}

# read in the results from the acoustic analysis on all audio files (including some excluded from the experiment)
audio_data <- read_excel("BabbleAcoustic/Acoustic_characteristics_dataset_age_language.xlsx")
audio_data2<- read_excel("BabbleAcoustic/Acoustic_characteristics_dataset_sex.xlsx",)
colnames(audio_data2)<-colnames(audio_data)
# combine into one dataset
audio_data<-rbind(audio_data,audio_data2)

# read in the age_language stimuli (as a string)
age_lang_stimuli_string<-paste(readLines("stimuli/age_language_test_stimuli.js"),collapse="")
# pull out the audio file names from the string (get a list of all audio files actually used)
age_lang_audio_file_list<-str_sub(string = age_lang_stimuli_string,start = str_locate_all(age_lang_stimuli_string,".wav")[[1]][,1]-10,end = str_locate_all(age_lang_stimuli_string,".wav")[[1]][,2])

# read in the sex stimuli (as a string)
sex_stimuli_string<-paste(readLines("stimuli/sex_test_stimuli.js"),collapse="")
# pull out the audio file names from the string (get a list of all audio files actually used)
sex_audio_file_list<-str_sub(string = sex_stimuli_string,start = str_locate_all(sex_stimuli_string,".wav")[[1]][,1]-10,end = str_locate_all(sex_stimuli_string,".wav")[[1]][,2])

# make list of stimuli actually used
audio_files_used<-c(age_lang_audio_file_list,sex_audio_file_list)

# confirm that all the used audio files are in the audio_data
#all(audio_files_used%in%paste0("0",audio_data$Filename,".wav"))

# attach the babies unique ID to the audio_data dataframe, and other data
for(i in 1:nrow(audio_data)){
  baby_data<-subset(metadata,metadata$clip_ID==paste0("0",audio_data$Filename[i],".wav"))
  audio_data$stim_ID[i]<-baby_data$unique_id
  audio_data$age_mo_round[i]<-baby_data$age_mo_round
  audio_data$gender[i]<-baby_data$child_gender
  audio_data$corpus[i]<-baby_data$corpus
  audio_data$language[i]<-baby_data$language
  audio_data$age_group[i]<-baby_data$age_groups
}

# make better column names
colnames(audio_data)<-c("Filename","duration","textgrdlabel","f0","f1","f2","intens","stim_ID","age_mo_round","gender","corpus","language","age_group")

# confirm data in the right format
audio_data$f0<-as.numeric(audio_data$f0)
audio_data$f1<-as.numeric(audio_data$f1)
audio_data$f2<-as.numeric(audio_data$f2)
audio_data$intens<-as.numeric(audio_data$intens)
audio_data$duration<-as.numeric(audio_data$duration)
audio_data$age_mo_round<-as.numeric(audio_data$age_mo_round)

audio_data$Filename<-as.factor(audio_data$Filename)
audio_data$stim_ID<-as.factor(audio_data$stim_ID)
audio_data$gender<-as.factor(audio_data$gender)
audio_data$corpus<-as.factor(audio_data$corpus)
audio_data$language<-as.factor(audio_data$language)
audio_data$age_group<-as.factor(audio_data$age_group)

# subset to the audio data for the age_lang questions
age_lang_sub_audio<-subset(audio_data,paste0("0",audio_data$Filename,".wav")%in%age_lang_audio_file_list)
# remove duplicates (because some files were used in both age_lang and sex)
age_lang_sub_audio<-age_lang_sub_audio[!duplicated(age_lang_sub_audio$Filename),]

# subset to the audio data for the sex questions
sex_sub_audio<-subset(audio_data,paste0("0",audio_data$Filename,".wav")%in%sex_audio_file_list)
# remove duplicates (because some files were used in both age_lang and sex)
sex_sub_audio<-sex_sub_audio[!duplicated(sex_sub_audio$Filename),]

```

This document responds to questions raised by reviewers during the review process. You will need to get the private metadata csv file from the BabbleCor authors (and our data) in order to reproduce these results.

This document reads in the results of an acoustic analysis and examines whether there are statistical differences on any of the f0, f1, f2, intensity, or duration measurements between the groups of babies as divided by the factors analyzed in the study.

We first analyze the data with list-wise deletion for missing cases (when one of the acoustic features could not be calculated), and then test two methods of multiple imputation (random sample from observed values and predictive mean matching).

As can be seen below, there are no statistically significant differences on any of the measurements (for either the Age/Language stimuli or the Sex stimuli) in any of the different methods of analysis. It seems unlikely that differences in participants judgements were based on these acoustic features. 

Note: the duration of audio clips does not reflect the duration of the original infant vocalizations. The BabbleCor clips were edited to be approximately ~400ms (under ~500ms).

\newpage

# List-wise Deletion

## Analysis of the Sex Stimuli

### f0 midpoint analysis

```{r}
par(mfrow = c(1,2))
boxplot(f0~gender,data = sex_sub_audio,
        main="f0 Gender Anlysis (Raw Data)",
        ylim = c(min(sex_sub_audio$f0,na.rm = T),
                 max(sex_sub_audio$f0,na.rm = T)),
        cex.main=0.75)
boxplot(f0~gender,data = aggregate(f0~gender*stim_ID,data = sex_sub_audio,mean),
        ylim = c(min(sex_sub_audio$f0,na.rm = T),
                 max(sex_sub_audio$f0,na.rm = T)),
        main = "f0 Gender Analysis (Participant Averages)",
        cex.main=0.75)
pander(summary(aov(f0~gender+Error(stim_ID), data = sex_sub_audio))[[1]])
```

\newpage

### f1 midpoint analysis

```{r}

par(mfrow = c(1,2))
boxplot(f1~gender,data = sex_sub_audio,main="f1 Gender Anlysis (Raw Data)",
        ylim = c(min(sex_sub_audio$f1,na.rm = T),
                 max(sex_sub_audio$f1,na.rm = T)),
        cex.main=0.75)
boxplot(f1~gender,data = aggregate(f1~gender*stim_ID,data = sex_sub_audio,mean),
        ylim = c(min(sex_sub_audio$f1,na.rm = T),
                 max(sex_sub_audio$f1,na.rm = T)),
        main = "f1 Gender Analysis (Participant Averages)",
        cex.main=0.75)
pander(summary(aov(f1~gender+Error(stim_ID), data = sex_sub_audio))[[1]])
```

\newpage

### f2 midpoint analysis

```{r}

par(mfrow = c(1,2))
boxplot(f2~gender,data = sex_sub_audio,main="f2 Gender Anlysis (Raw Data)",
        ylim = c(min(sex_sub_audio$f2,na.rm = T),
                 max(sex_sub_audio$f2,na.rm = T)),
        cex.main=0.75)
boxplot(f2~gender,data = aggregate(f2~gender*stim_ID,data = sex_sub_audio,mean),
        ylim = c(min(sex_sub_audio$f2,na.rm = T),
                 max(sex_sub_audio$f2,na.rm = T)),
        main = "f2 Gender Analysis (Participant Averages)",
        cex.main=0.75)
pander(summary(aov(f2~gender+Error(stim_ID), data = sex_sub_audio))[[1]])

```

\newpage

### intensity analysis

```{r}
par(mfrow = c(1,2))
boxplot(intens~gender,data = sex_sub_audio,
        main="intensity Gender Anlysis (Raw Data)",
        ylim = c(min(sex_sub_audio$intens,na.rm = T),
                 max(sex_sub_audio$intens,na.rm = T)),
        cex.main=0.75)
boxplot(intens~gender,data = aggregate(intens~gender*stim_ID,data = sex_sub_audio,mean),
        ylim = c(min(sex_sub_audio$intens,na.rm = T),
                 max(sex_sub_audio$intens,na.rm = T)),
        main = "intensity Gender Analysis (Participant Averages)",
        cex.main=0.75)
pander(summary(aov(intens~gender+Error(stim_ID), data = sex_sub_audio))[[1]])
```

\newpage

### duration midpoint analysis

```{r}
par(mfrow = c(1,2))
boxplot(duration~gender,data = sex_sub_audio,
        main="duration Gender Anlysis (Raw Data)",
        ylim = c(min(sex_sub_audio$duration,na.rm = T),
                 max(sex_sub_audio$duration,na.rm = T)),
        cex.main=0.75)
boxplot(duration~gender,data = aggregate(duration~gender*stim_ID,data = sex_sub_audio,mean),
        ylim = c(min(sex_sub_audio$duration,na.rm = T),
                 max(sex_sub_audio$duration,na.rm = T)),
        main = "duration Gender Analysis (Participant Averages)",
        cex.main=0.75)
pander(summary(aov(duration~gender+Error(stim_ID), data = sex_sub_audio))[[1]])
```

\newpage

## Analysis of the Age/Language Stimuli

### f0 midpoint analysis

```{r}
par(mfrow = c(1,2),mar=c(10,4,1,1))
boxplot(f0~age_group*language,data = age_lang_sub_audio,
        main="f0 Gender Anlysis (Raw Data)",
        ylim = c(min(age_lang_sub_audio$f0,na.rm = T),
                 max(age_lang_sub_audio$f0,na.rm = T)),
        cex.main=0.75,
        las=2,
        xlab = "")
boxplot(f0~age_group*language,
        data = aggregate(f0~age_group*language*stim_ID,data = age_lang_sub_audio,mean),
        ylim = c(min(age_lang_sub_audio$f0,na.rm = T),
                 max(age_lang_sub_audio$f0,na.rm = T)),
        main = "f0 Gender Analysis (Participant Averages)",
        cex.main=0.75,
        las=2,
        xlab = "")
pander(summary(aov(f0~age_group*language+Error(stim_ID), data = age_lang_sub_audio))[[1]])
```

\newpage

### f1 midpoint analysis

```{r}

par(mfrow = c(1,2),mar=c(10,4,1,1))
boxplot(f1~age_group*language,data = age_lang_sub_audio,
        main="f1 Gender Anlysis (Raw Data)",
        ylim = c(min(age_lang_sub_audio$f1,na.rm = T),
                 max(age_lang_sub_audio$f1,na.rm = T)),
        cex.main=0.75,
        las=2,
        xlab = "")
boxplot(f1~age_group*language,
        data = aggregate(f1~age_group*language*stim_ID,data = age_lang_sub_audio,mean),
        ylim = c(min(age_lang_sub_audio$f1,na.rm = T),
                 max(age_lang_sub_audio$f1,na.rm = T)),
        main = "f1 Gender Analysis (Participant Averages)",
        cex.main=0.75,
        las=2,
        xlab = "")
pander(summary(aov(f1~age_group*language+Error(stim_ID), data = age_lang_sub_audio))[[1]])
```

\newpage

### f2 midpoint analysis

```{r}
par(mfrow = c(1,2),mar=c(10,4,1,1))
boxplot(f2~age_group*language,data = age_lang_sub_audio,
        main="f2 Gender Anlysis (Raw Data)",
        ylim = c(min(age_lang_sub_audio$f2,na.rm = T),
                 max(age_lang_sub_audio$f2,na.rm = T)),
        cex.main=0.75,
        las=2,
        xlab = "")
boxplot(f2~age_group*language,
        data = aggregate(f2~age_group*language*stim_ID,data = age_lang_sub_audio,mean),
        ylim = c(min(age_lang_sub_audio$f2,na.rm = T),
                 max(age_lang_sub_audio$f2,na.rm = T)),
        main = "f2 Gender Analysis (Participant Averages)",
        cex.main=0.75,
        las=2,
        xlab = "")
pander(summary(aov(f2~age_group*language+Error(stim_ID), data = age_lang_sub_audio))[[1]])
```

\newpage

### intensity analysis

```{r}
par(mfrow = c(1,2),mar=c(10,4,1,1))
boxplot(intens~age_group*language,data = age_lang_sub_audio,
        main="intensity Gender Anlysis (Raw Data)",
        ylim = c(min(age_lang_sub_audio$intens,na.rm = T),
                 max(age_lang_sub_audio$intens,na.rm = T)),
        cex.main=0.75,
        las=2,
        xlab = "")
boxplot(intens~age_group*language,
        data = aggregate(intens~age_group*language*stim_ID,data = age_lang_sub_audio,mean),
        ylim = c(min(age_lang_sub_audio$intens,na.rm = T),
                 max(age_lang_sub_audio$intens,na.rm = T)),
        main = "intensity Gender Analysis (Participant Averages)",
        cex.main=0.75,
        las=2,
        xlab = "")
pander(summary(aov(intens~age_group*language+Error(stim_ID), data = age_lang_sub_audio))[[1]])
```

\newpage

### duration midpoint analysis

```{r}
par(mfrow = c(1,2),mar=c(10,4,1,1))
boxplot(duration~age_group*language,
        data = age_lang_sub_audio,
        main="duration Gender Anlysis (Raw Data)",
        ylim = c(min(age_lang_sub_audio$duration,na.rm = T),
                 max(age_lang_sub_audio$duration,na.rm = T)),
        cex.main=0.75,
        las=2,
        xlab = "")
boxplot(duration~age_group*language,
        data = aggregate(duration~age_group*language*stim_ID,data = age_lang_sub_audio,mean),
        ylim = c(min(age_lang_sub_audio$duration,na.rm = T),
                 max(age_lang_sub_audio$duration,na.rm = T)),
        main = "duration Gender Analysis (Participant Averages)",
        cex.main=0.75,
        las=2,
        xlab = "")
pander(summary(aov(duration~age_group*language+Error(stim_ID), data = age_lang_sub_audio))[[1]])
```

\newpage

# Multiple Imputation (Sample Observed Values)

## Analysis of the Sex Stimuli

```{r, include=FALSE}
# Fill in empty data by random sample from observed values
MI<-mice(data = sex_sub_audio[,c("duration","f0","f1","f2","intens",
                                 "stim_ID","age_mo_round","gender",
                                 "corpus","language","age_group")],
         method = "sample",maxit = 10) # specifying columns for consistency with age/language stimuli analysis where there were problems with the Filename column
MI_List<-mids2mitml.list(MI)
```

### f0 midpoint analysis

```{r}
fit1<-with(MI_List,lmer(f0~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f0~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

### f1 midpoint analysis

```{r}
fit1<-with(MI_List,lmer(f1~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f1~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

### f2 midpoint analysis

```{r}
fit1<-with(MI_List,lmer(f2~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f2~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

### intensity analysis

```{r}
fit1<-with(MI_List,lmer(intens~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(intens~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

### duration midpoint analysis

```{r}
fit1<-with(MI_List,lmer(duration~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(duration~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

## Analysis of the Age/Langurage Stimuli

```{r, include=FALSE}
# Fill in empty data by random sample from observed values
MI<-mice(data = age_lang_sub_audio[,c("duration","f0","f1","f2","intens",
                                      "stim_ID","age_mo_round","gender",
                                      "corpus","language","age_group")],
         method = "sample",maxit = 10) # the Filename column causes the program to stall so specify all the other columns (expect textgrdlabel because it holds no possible interest)
MI_List<-mids2mitml.list(MI)
```

### f0 midpoint analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(f0~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f0~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(f0~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(f0~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```

\newpage

### f1 midpoint analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(f1~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f1~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(f1~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(f1~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```

\newpage

### f2 midpoint analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(f2~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f2~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(f2~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(f2~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```

\newpage

### intensity analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(intens~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(intens~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(intens~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(intens~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```

\newpage

### duration midpoint analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(duration~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(duration~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(duration~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(duration~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```

\newpage

# Multiple Imputation (Predictive Mean Matching)

## Analysis of the Sex Stimuli

```{r, include=FALSE}
# Fill in empty data by predictive mean matching
MI<-mice(data = sex_sub_audio[,c("duration","f0","f1","f2","intens",
                                 "stim_ID","age_mo_round","gender",
                                 "corpus","language","age_group")],
         method = "pmm",maxit = 10) # specifying columns for consistency with age/language stimuli analysis where there were problems with the Filename column
MI_List<-mids2mitml.list(MI)
```

### f0 midpoint analysis

```{r}
fit1<-with(MI_List,lmer(f0~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f0~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

### f1 midpoint analysis

```{r}
fit1<-with(MI_List,lmer(f1~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f1~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

### f2 midpoint analysis

```{r}
fit1<-with(MI_List,lmer(f2~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f2~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

### intensity analysis

```{r}
fit1<-with(MI_List,lmer(intens~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(intens~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

### duration midpoint analysis

```{r}
fit1<-with(MI_List,lmer(duration~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(duration~1+gender+(1|stim_ID)))
testModels(fit2,fit1)
```

\newpage

## Analysis of the Age/Langurage Stimuli

```{r, include=FALSE}
# Fill in empty data by predictive mean matching
MI<-mice(data = age_lang_sub_audio[,c("duration","f0","f1","f2","intens",
                                      "stim_ID","age_mo_round","gender",
                                      "corpus","language","age_group")],
         method = "pmm",maxit = 10) # the Filename column causes the program to stall so specify all the other columns (expect textgrdlabel because it holds no possible interest)
MI_List<-mids2mitml.list(MI)
```

### f0 midpoint analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(f0~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f0~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(f0~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(f0~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```

\newpage

### f1 midpoint analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(f1~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f1~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(f1~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(f1~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```

\newpage

### f2 midpoint analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(f2~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(f2~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(f2~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(f2~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```

\newpage

### intensity analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(intens~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(intens~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(intens~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(intens~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```

\newpage

### duration midpoint analysis

```{r, message=FALSE}
fit1<-with(MI_List,lmer(duration~1+(1|stim_ID)))
fit2<-with(MI_List,lmer(duration~1+age_group+(1|stim_ID)))
fit3<-with(MI_List,lmer(duration~1+age_group+language+(1|stim_ID)))
fit4<-with(MI_List,lmer(duration~1+age_group*language+(1|stim_ID)))
testModels(fit2,fit1)
testModels(fit3,fit2)
testModels(fit4,fit3)
```